Benchmarking FDR Methods - Simulation Summarized ROC / UpsetR Plots

### 2018-01-19 datasets/simulations/analysis-05-psim-subsetonly.Rmd
Fix typo

"M100/esize_fixed-bl-uniform-0.95/results-alteff_30-M100.rds" %>%
    file.path("data-psim-parsed", .) %>%
    readRDS() %>%
    preclean() %>%
    myplot() + 
    ggtitle("Distribution: normal, pi0: 95% (100 replications)")

"M100/esize_fixed-bl-uniform-0.99/results-alteff_30-M100.rds" %>%
    file.path("data-psim-parsed", .) %>%
    readRDS() %>%
    preclean() %>%
    myplot() + 
    ggtitle("Distribution: normal, pi0: 99% (100 replications)")
```

>>>>

"M100/esize_fixed-uniform-0.95/results-alteff_30-M100.rds" %>%
    file.path("data-psim-parsed", .) %>%
    readRDS() %>%
    preclean() %>%
    myplot() + 
    ggtitle("Distribution: normal, pi0: 95% (100 replications)")

"M100/esize_fixed-uniform-0.99/results-alteff_30-M100.rds" %>%
    file.path("data-psim-parsed", .) %>%
    readRDS() %>%
    preclean() %>%
    myplot() + 
    ggtitle("Distribution: normal, pi0: 99% (100 replications)")
```
